Crawler and Inverted Index in Java

### 2023-11-05 latexJava/paperJava.tex
Edit Indexer section in paper

\item 
The \texttt{IndexerState} enumeration defines various states that may occur during the tokenization of a document's text. States such as \textit{InToken}, \textit{InInvalidTokenUnknownEnd}, \textit{InInvalidToken}, and \textit{OutOfToken} describe different tokenization scenarios.

\item
The \texttt{Indexer} class is responsible for creating an inverted index based on documents stored in the \texttt{FileDatalake} and storing it in the \texttt{Datamart}. The class provides the following functionalities:

\begin{itemize}
  \item \texttt{tokenize(String document)}: Tokenizes the text content of a document, splitting it into individual words (tokens), removing punctuation, and preparing tokens for indexing.
  \item \texttt{index()}: Initiates the indexing process. It creates an inverted index from the available documents in the \texttt{FileDatalake} and stores it in the \texttt{Datamart}.
\end{itemize}

\item
The \texttt{IndexerTest} class contains a set of unit tests for the \texttt{Indexer} class. These tests verify the correct behavior of the \texttt{tokenize} method in various scenarios (such as checking if it copes with underscores  at the beginning or at the end of words), ensuring the accuracy of tokenization.
\end{itemize}

Finally the \texttt{Main} class serves as the entry point for the program. It accepts two command-line arguments: the path to the \texttt{datalake} (data source) and \texttt{datamart} (destination for the inverted index). The program creates instances of \texttt{FileDatalake} and \texttt{Datamart} and then initiates the indexing process using the \texttt{Indexer} class.

>>>>

\item
The \texttt{Indexer} class is responsible for creating an inverted index based on documents stored in the \texttt{FileDatalake} and storing it in the \texttt{Datamart}, with the actual implementation being injected as a dependency on creation. The class provides the following functionalities:

\begin{itemize}
  \item \texttt{tokenize(String document)}: Tokenizes the text content of a document, this is done using a state machine pattern that processes the text character by character, trying to be much more efficient than a regular expression.
		It returns a set of tokens found in the document.
  \item \texttt{index()}: Initiates the indexing process. It creates an inverted index from the available documents in the \texttt{FileDatalake} and stores it in the \texttt{Datamart}.
		After it finishes, it blocks in a loop, listening in on new documents being added to the datalake, and updating the index accordingly as they are added.
\end{itemize}

\item 
The \texttt{IndexerState} enumeration defines the states for the tokenization state machine used by the \texttt{Indexer} class. The states are as follows:

\begin{itemize}
	\item \texttt{OutOfToken} The state machine is not currently processing a token.
	\item \texttt{InToken} The state machine is currently processing a token.
	\item \texttt{InValidTokenUnknownEnd} The state machine is in an ambiguous position, where whenever the current token ends early or continues depends on future characters.
	\item \texttt{InInvalidToken} The state machine is currently processing an invalid token, and thus should ignore future valid characters until the token ends.
		This can for example occur when the token is too long, as no one is going to search for tokens that are many times longer than an average word.
\end{itemize}
\end{itemize}

Finally the \texttt{Main} class serves as the entry point for the program. It accepts two command-line arguments: the path to the \texttt{datalake} (data source) and \texttt{datamart} (destination for the inverted index).
The program creates instances of \texttt{FileDatalake} and an instance the \texttt{Datamart} and then initiates the indexing process using the \texttt{Indexer} class.
Aditionally, this module has various unit tests for ensuring the correctness and robustness of the tokenization implementation,
as this part is the most complex and error-prone in the project, especially considering that it deals with any arbitrary unvetted text coming in from the internet.
